Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-20 papers/clusters.tex
Typos, a word, and comma for large numbers

% results
\newcommand{\totalnumber}{98462}

@@

Part of the reason that chemical tagging still remains unrealized
is because the level of abundance specificity required
is very high.
If there are thousands of (relevant) molecular clouds forming stars in
the recent history of the Milky Way, clumps of stars can only be
identified in abundance space if abundance space is high in dimensionality.
(In principle, it needs to be high in dimensionality both in terms
of the number of measured abundances \emph{and} in terms of the number of
nucleosynthetic pathways or the dimensionality of the true abundance
space.)
Therefore accurate---or at
least precise---measurements of many different abundances are needed
for stellar sibling to have sufficiently unique fingerprints.
Stellar spectroscopic surveys now have the resolution,
$S/N$, wavelength coverage, and sample sizes to deliver many
different chemical tags for each star.

@@

Our analysis draws on the spectra of \totalnumber\ giant stars ($\logg
< 3.9$) from \apogee\ \acronym{DR12} \citep{dr12}, with no warning flags
set in the \apogee\ \aspcap\ \citep{aspcap} pipeline
reductions.
We re-analyze these \emph{spectra} using \thecannon, because this
deliver stellar abundance labels of higher precision, especially for
stars of $S/N \le 150$.
The details about how we select, reduce, and analyze the \apogee\ data
are given in full detail in the companion papers \citep{casey16,
  ness16}, and we only summarize briefly here.
We re-derived 17 labels ($\teff$, $\logg$, and 15 abundances
referenced to H) form the \apogee\ \acronym{DR12} spectra. 
For the training step of \thecannon, 
12,681 red-giant stars with spectral $S/N \ge 200$ were used.
For this small fraction of the sample with the highest $S/N$ objects the
labels provided by \aspcap\ provide consistent, relatively low-scatter, sensible
abundance-space measurements.
The training step fixes a spectral model
that predicts the normalized spectrum as a quadratic function of all
labels. In the second stage---the test step---each unlabelled star is
used to establish a single-star likelihood function for its labels,
holding the model coefficients fixed.
\thecannon\ finds the labels that minimize the single-star likelihood
function for each test-set star.
This optimization is not convex, but it is embarrassingly parallel,
and therefore fast. The test
step for 150,000 spectra takes less than 30~minutes on a small 
research cluster in Cambridge.

>>>>

% results
\newcommand{\totalnumber}{98,462}

@@

Part of the reason that chemical tagging remains unrealized
is because the level of abundance specificity required
is very high.
If there are thousands of (relevant) molecular clouds forming stars in
the recent history of the Milky Way, clumps of stars can only be
identified in abundance space if abundance space is high in dimensionality.
(In principle, it needs to be high in dimensionality both in terms
of the number of measured abundances \emph{and} in terms of the number of
nucleosynthetic pathways or the dimensionality of the true abundance
space.)
Therefore accurate---or at
least precise---measurements of many different abundances are needed
for stellar sibling to have sufficiently unique fingerprints.
Stellar spectroscopic surveys now have the resolution,
$S/N$, wavelength coverage, and sample sizes to deliver many
different chemical tags for each star.

@@

Our analysis draws on the spectra of \totalnumber\ giant stars ($\logg
< 3.9$) from \apogee\ \acronym{DR12} \citep{dr12}, with no warning flags
set in the \apogee\ \aspcap\ \citep{aspcap} pipeline
reductions.
We re-analyze these \emph{spectra} using \thecannon, because this
deliver stellar abundance labels of higher precision, especially for
stars of $S/N \le 150$.
The details about how we select, reduce, and analyze the \apogee\ data
are given in full detail in the companion papers \citep{casey16,
  ness16}, and we only summarize briefly here.
We re-derived 17 labels ($\teff$, $\logg$, and 15 abundances
referenced to H) from the \apogee\ \acronym{DR12} spectra. 
For the training step of \thecannon, 
12,681 red-giant stars with spectral $S/N \ge 200$ were used.
For this small fraction of the sample with the highest $S/N$, the
labels provided by \aspcap\ provide consistent, relatively low-scatter, sensible
abundance-space measurements.
The training step fixes a spectral model
that predicts the normalized spectrum as a quadratic function of all
labels. In the second stage---the test step---each unlabelled star is
used to establish a single-star likelihood function for its labels,
holding the model coefficients fixed.
\thecannon\ finds the labels that minimize the single-star likelihood
function for each test-set star.
This optimization is not convex, but it is embarrassingly parallel,
and therefore fast. The test
step for 150,000 spectra takes less than 30~minutes on a small 
research cluster in Cambridge.
